Data Preparation - Course Catalogues

### 2019-04-15 Data Preparation - Course Catalogues.Rmd
Adds MSP catalogue

overview_section_start <- function(string) string %>% str_detect(pattern = "^ *Core Courses")
overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\n *Maastricht Science Programme")

headers_UCM_UCV <- c("^ *Core Courses",
                     "^Humanities \\(HUM\\)",
                     "^ *Life Sciences Courses",
                     "^Sciences \\(SCI\\)",
                     "^ *Social Sciences",
                     "^ *Skills Trainings",
                     "^ *Projects",
                     "^Undergraduate Research",
                     "Appendix") %>% collapse_or
is_header     <- function(string) string %>% str_detect(pattern = headers_UCM_UCV)

course_code_UCM_UCV <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP", # UCM
                         "VCO", "VSC", "VSS", "VSK", "VPR", "VCA" # UCV
                         ) %>% collapse_or
overview_start  <- function(string) string %>% extract_id_course %>% str_detect(pattern = course_code_UCM_UCV) # simplify with %in% course_code_UCM
```

@@

```{r d_text$catalogues}
d_text$catalogues <- tribble(
  ~ ID              ,  ~ page_top                  , ~ before_overview                       ,
  "European_studies", "^.Bachelor European Studies", "Faculty of Arts and Social Sciences"   ,
  "Psychology"      , "^.Bachelor Psychology"      , "Faculty of Psychology and Neuroscience",
  "UCV"             , NA_character_                , NA_character_                           ,
  "UCM"             , NA_character_                , NA_character_                                   
  ) %>%

@@

## UCM, UCV

@@

```{r overview_UCM}
overview_UCM_UCV <- function(catalogue, ID){

@@

  # paste current page and following page (`lead(page)`) if overview is two page long
  transmute(text        = list(page, lead(page)) %>% pmap_chr(paste_if_2_page_overview),
         `Course ID` = text %>% extract_id_course) %>%
    mutate(department  = ID) %>%
    filter(!is.na(text))

@@

  }else if(ID %in% c("UCM", "UCV")){
    catalogue %>% overview_UCM_UCV(ID = ID)

  }else "to do"

@@

@@

```{r}
save(d_text, file = "Output/d_text.RDATA")
```

>>>>

overview_section_start <- function(string) string %>% str_detect(pattern = "^ *Core Courses|^ *Mathematics and")
overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\n *Maastricht Science Programme|^*Courses Available at University")

headers_UCM_UCV_MSP <- c("^ *Core Courses",
                     "^Humanities \\(HUM\\)",
                     "^ *Life Sciences Courses",
                     "^Sciences \\(SCI\\)",
                     "^ *Social Sciences",
                     "^ *Skills Trainings",
                     "^ *Projects",
                     "^Undergraduate Research",
                     "Appendix",
                     "^ *Mathematics and") %>% collapse_or
is_header     <- function(string) string %>% str_detect(pattern = headers_UCM_UCV_MSP)

course_code_UCM_UCV_MSP <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP", # UCM
                         "VCO", "VSC", "VSS", "VSK", "VPR", "VCA", # UCV
                         "BIO", "CHE", "MAT", "PHY", "NEU", "INT", "PRA" #MSP
                         ) %>% collapse_or
overview_start  <- function(string) string %>% extract_id_course %>% str_detect(pattern = course_code_UCM_UCV_MSP) # simplify with %in% course_code_UCM
```

@@

```{r d_text$catalogues}
d_text$catalogues <- tribble(
  ~ ID              ,  ~ page_top                  , ~ before_overview                       ,
  "European_studies", "^.Bachelor European Studies", "Faculty of Arts and Social Sciences"   ,
  "Psychology"      , "^.Bachelor Psychology"      , "Faculty of Psychology and Neuroscience",
  "UCV"             , NA_character_                , NA_character_                           ,
  "UCM"             , NA_character_                , NA_character_                           ,
  "MSP"             , NA_character_                , NA_character_
  ) %>%

@@

## UCM, UCV, MSP

@@

```{r overview_UCM}
overview_UCM_UCV_MSP <- function(catalogue, ID){

@@

  # paste current page and following page (`lead(page)`) if overview is two page long
  transmute(
    text        = list(page, lead(page)) %>% pmap_chr(paste_if_2_page_overview),
    `Course ID` = text %>% extract_id_course) %>%
    mutate(department  = ID) %>%
    filter(!is.na(text))

@@

  }else if(ID %in% c("UCM", "UCV", "MSP")){
    catalogue %>% overview_UCM_UCV_MSP(ID = ID)

  } else "to do"

@@

# Current course
```{r}
course_current <- d_text$catalogues %>% filter(department == "UCM") %>% distinct(`Course ID`) %>% pull
```

@@

```{r}
save(course_current, file = "Output/course_current.RDATA")
save(d_text        , file = "Output/d_text.RDATA")
```
